Computational Six-bar Synthesis for Implementing Dynamic Behavior

### 2019-03-18 draft.tex
New fixes from Ron's 3/16/19 email

Achieving high performance dynamic behavior in a robot requires careful design of morphology.
While optimization methods are frequently used to perform design, 
searching for a global optimum in an intensely nonlinear and high-dimensional design space is difficult, 
especially if stochastic seeding is involved.  
In contrast to optimal synthesis, the role of design exploration is to survey a multitude of solutions over the entirety of the design space.
Rather than using optimization, in this work, design requirements are encoded into a square system of equations that manifests the design space's nonlinearities.  
Due to these nonlinearities, this system will possess a huge number of isolated roots.  
Each root contains a description of robot geometry, thus their discovery becomes the action of design.  
Following this, the computation of all isolated roots constitutes design space exploration.  
These systems are heavily burdened with infinite roots, a type of degenerate root, resulting in a small percentage of physically relevant roots.  
A recently developed algorithm termed Finite Root Generation relieves this burden. 
In this paper, we obtain all isolated roots for a certain six-bar design problem for the first time.  
Six-bar motions offer a level of complexity that make this topology particular viable.  
The type of synthesis enabled here allows the design of a transmission function from motor dynamics to a loaded end effector to influence overall dynamic behavior.
Design exploration is demonstrated for a robotic leg prototype.
We extracted from 1,528,608 million isolated roots 941 physically relevant cognate foursomes that expand into 3764 mechanism designs before defects.
This work in the plane provides solid foundations for generalizations into spatial mechanisms.
\end{abstract}

@@

{\color{ForestGreen}
Our treatment of design involves dealing with algebraic equations rather than geometric constructions.
This makes our method technically simple for designers without prior knowledge of mechanism parameters, removing the need for geometric creativity.
Furthermore, by generating multiple design options, a designer is better equipped to account for secondary requirements, such as sensitivity to fabrication errors.
}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.4]{synth_results_first}
\hfil
\vspace{5mm}
\includegraphics[scale=0.4]{synth_results_second}
\caption{Linkage designs that exhibit the desired dynamic behavior.  Linkages (a) and (b) are cognates that trace the exact same path with the same coordination of mechanical advantage over arc length.  The same goes for (c) and (d).}
\label{synth_results}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{PointByPointDeviation}
\caption{The variation in mechanical advantage due to deviations in individual pivot locations for mechanisms shown in Fig. \ref{synth_results}.  Columns correspond to mechanisms (a), (b), (c), and (d).  Rows correspond to pivots $A$, $B$, $C$, $D$, $F$, $G$, and $H$.  Deviations simulate fabrication errors from the pivots' ideal locations.  Deviations were parameterized with polar coordinates.  Polar radii are indicated by line color, and polar angles are varied on the horizontal axes.  Note that if the absolute value of mechanical advantage is zero, this indicates that the deviation resulted in a branch defective linkage.  Column (a) and column (b) respectively indicate designs sensitive and insensitive to position errors.  Deviation of pivot $A$ had little effect on the resulting mechanical advantage.  Deviation of pivot $F$ had a large effect.}
\label{PointByPointDeviation}
\end{figure}

@@

To understand the effect that errors in pivot positions has on the low MA value, we shifted pivot positions off from their ideal values, given in Table \ref{linkage_solution_numbers}.
Deviations were introduced to each pivot individually, and were parameterized by polar coordinates.
Offset radii of 0.05 cm, 0.10 cm, 0.15 cm, and 0.20 cm were swept from 0 to 2$\pi$.
For each offset, the resulting deviated linkage was analyzed and its low MA value was computed.
Deviation results for the four linkages shown in Fig. \ref{synth_results} are shown in Fig. \ref{PointByPointDeviation}.
At times, the low MA value computed to zero.
This indicates that a deviated linkage encountered a singular configuration and is thus branch defective.
For our application, these dimensional errors would be problematic.
In application, they would bring the motor to stall as the linkage jams.
On the other hand, if the low MA value is too high, power modulation will not occur.
Referring to Fig. \ref{PointByPointDeviation}, our analysis indicates mechanism (a) to be the most sensitive to dimensional errors, and mechanism (b) to be the least sensitive.
Across all designs, pivot $F$ was the most sensitive to dimensional errors, and pivot $A$ was the least sensitive.

>>>>

Achieving high performance dynamic behavior in a robot requires careful design of morphology.
While optimization methods are frequently used to perform design, 
searching for a global optimum in an intensely nonlinear and high-dimensional design space is difficult, 
especially if stochastic seeding is involved.  
In contrast to optimal synthesis, the role of design exploration is to survey a multitude of solutions over the entirety of the design space.
Rather than using optimization, in this work, design requirements are encoded into a square system of equations that manifests the design space's nonlinearities.  
Due to these nonlinearities, this system will possess a huge number of isolated roots.  
Each root contains a description of robot geometry, thus their discovery becomes the action of design.  
Following this, the computation of all isolated roots constitutes design space exploration.  
These systems are heavily burdened with infinite roots, a type of degenerate root, resulting in a small percentage of physically relevant roots.  
A recently developed algorithm termed Finite Root Generation relieves this burden. 
In this paper, we obtain all isolated roots for a certain six-bar design problem for the first time.  
Six-bar motions offer a level of complexity that make this topology particular viable.  
The type of synthesis enabled here allows the design of a transmission function from motor dynamics to a loaded end effector to influence overall dynamic behavior.
Design exploration is demonstrated for a robotic leg prototype.
We extracted from 1,528,608 million isolated roots 941 physically relevant cognate foursomes that expand into 3764 mechanism designs before defects.
%This work in the plane provides solid foundations for generalizations into spatial mechanisms.
\end{abstract}

@@

Our treatment of design involves dealing with algebraic equations rather than geometric constructions.
This makes our method technically simple for designers without prior knowledge of mechanism parameters, removing the need for geometric creativity.
Furthermore, by generating multiple design options, a designer is better equipped to account for secondary requirements, such as sensitivity to fabrication errors.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.4]{synth_results_first}
\hfil
\vspace{5mm}
\includegraphics[scale=0.4]{synth_results_second}
\caption{Linkage designs that exhibit the desired dynamic behavior.  Linkages (a) and (b) are cognates that trace the exact same path with the same coordination of mechanical advantage over arc length.  The same goes for (c) and (d).   Moving pivots are drawn in displaced positions $C'$, $D'$, $F'$, $G'$, $H'$.  Home position values are listed in Table \ref{linkage_solution_numbers}.}
\label{synth_results}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{PointByPointDeviation}
\caption{The variation in mechanical advantage due to deviations in individual pivot locations for mechanisms shown in Fig. \ref{synth_results}.  Columns correspond to mechanisms (a), (b), (c), and (d).  Rows correspond to pivots $A$, $B$, $C$, $D$, $F$, $G$, and $H$.  Deviations simulate fabrication errors from the pivots' ideal locations.  Deviations were parameterized with polar coordinates.  Polar radii are indicated by line color, and polar angles are varied on the horizontal axes.  Note that if mechanical advantage is zero, this indicates that the deviation resulted in a branch defective linkage.  Column (a) and column (b) respectively indicate designs sensitive and relatively insensitive to position errors.  Deviation of pivot $A$ had little effect on the resulting mechanical advantage.  Deviation of pivot $F$ had a large effect.}
\label{PointByPointDeviation}
\end{figure}

@@

To understand the effect that errors in pivot positions have on the low MA value, we shifted pivot positions off from their ideal values, given in Table \ref{linkage_solution_numbers}.
Deviations were introduced to each pivot individually, and were parameterized by polar coordinates.
Offset radii of 0.05 cm, 0.10 cm, 0.15 cm, and 0.20 cm were swept from 0 to 2$\pi$.
For each offset, the resulting deviated linkage was analyzed and its low MA value was computed.
Deviation results for the four linkages shown in Fig. \ref{synth_results} are shown in Fig. \ref{PointByPointDeviation}.
At times, the low MA value computed to zero.
This indicates that a deviated linkage encountered a singular configuration and is thus branch defective.
For our application, these dimensional errors would be problematic.
In application, they would bring the motor to stall as the linkage jams.
On the other hand, if the low MA value is too high, power modulation will not occur.
Referring to Fig. \ref{PointByPointDeviation}, our analysis indicates mechanism (a) to be the most sensitive to dimensional errors, and mechanism (b) to be the least sensitive.
Across all designs, pivot $F$ was the most sensitive to dimensional errors, and pivot $A$ was the least sensitive.
